Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/results.tex
updated figs of chap 5

\subsection{3D Exploration Setup and Paramaters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaces with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment took place at The George Washington University's (GWU) Science and Engineering Hall (SEH). This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-2.0$ m to $2.0$ m, the y-direction (positive north) spans $-2.0$ m to $2.0$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m.

>>>>

\subsection{3D Exploration Setup and Paramaters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaces with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment took place at the Flight Dynamics and Control Lab (FDCL) inside the second floor of SEH. This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-2.0$ m to $2.0$ m, the y-direction (positive north) spans $-2.0$ m to $2.0$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m.
